Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos

### 2014-02-13 paper/main.tex
fixing the abstract

We study
the alignment of DM halos with the cosmic web as described by the
tidal and velocity shear fields. We focus on the alignment of halos
shape, spin and peculiar velocities. We use a cosmological N-body
simulation that allows to study dark matter halos spanning four orders
of magnitude in mass ($(10^{10}$-$10^{14}$) \hMsun and spatial
scales of $(0.5$-$1.0)$\hMpc to define the cosmic web. After varying
the numerical parameters in our experiments we find that the tidal
field provides a robust description for the different kinds of
alignments.  We measure a strong here is a strong alignment of the
peculiar velocity field and the halo shape with the cosmic web defined
by the tidal field. The results for the spin alignment are less
significant. The shape alignment is stronger for halos that are either
 massive ($M>10^{12}$\hMsun), have large or are located in high
 density regions.

>>>>

We study the alignment of dark matter halos with the cosmic web as described by
the tidal and velocity shear fields. We focus on the alignment of their
shape, angular momentum and peculiar velocities. We use a cosmological N-body
simulation that allows to study dark matter halos spanning almost five orders
of magnitude in mass ($10^{9}$-$10^{14}$) \hMsun over spatial scales
of $(0.5$-$1.0)$\hMpc to define the cosmic web. After varying the
numerical parameters in our experiments we find that the strongest
alignment is measured for the halo shape with respect to the web
defined by the tidal field, with a stronger signal as the halo mass
increases. For the angular momentum we find weaker alignment signals for
halos more massive than $10^{12}$\hMsun both in the tidal and velocity
shear descriptions. The peculiar velocities of halos show a strong
alignment signal for the tidal web at all halo masses, while in the
velocity shear description the signal is weaker an only present for
halos less massive than $10^{12}$\hMsun. We also find that the main
directions of stronger tidal tension and velocity shear coincide for
halos below $10^{12}$\hMpc but are perpendicular to each other for
halos more massive than this threshold.
